Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-05-13 icdm/submission/includes/evaluation.tex
summary evaluation reworked

To summarize, we deleted words that appear very often (subsampling) and very infrequently (min count) from our dataset, i.e text8 dataset. To evaluate our word embeddings we defined the cosine distance and will measure the quality of our embeddings by comparing theim  to a human judged dataset of word pairs, based on their similarity, i.e wordsim353. The reader was also given an explanation about the configuration of our network and introduced to the concept of input shuffling. With all this knowledge we can know present the achieved experimental results in the next section.

>>>>

To summarize the evaluation, we deleted words that appear very often (subsampling) and very infrequently (min count) from our dataset, i.e text8 dataset. To evaluate the resulting word embeddings we defined the cosine distance, which is 1 minuse the cosine of the angle of two vectors. We will measure the quality of the embeddings by analyzing the correlation of the cosine distance of pairs of vectors to humanly judged similarity score of the corresponding words, and used the wordsim353 to collect these scores. The reader was also given an explanation about the configuration of our network and introduced to the concept of input shuffling. With all this knowledge we can know present the achieved experimental results in the next section.
